Cochain level May--Steenrod operations

### 2021-08-28 may_st.tex
Update references and split-off acks
Add hyperref to email addresses

\author[R. Kaufmann]{Ralph M.\ Kaufmann}
\address{R. Kaufmann, Department of Mathematics, Department of Physics and Astronomy, Purdue University}
\email{rkaufman@purdue.edu}

\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
\address{A. Medina-Mardones, Max Planck Institute for Mathematics \and
	University of Notre Dame du Lac}
\email{ammedmar@mpim-bonn.mpg.de}

@@

\begin{document}
	\input{aux/abstract}
	\maketitle
	\input{sec/introduction}
	\input{sec/preliminaries}
	\input{sec/groups}
	\input{sec/operads}
	\input{sec/steenrod}
	\input{sec/effective}
	\input{sec/outlook}
	\printbibliography
\end{document}

>>>>

\author[R.~Kaufmann]{Ralph~M.~Kaufmann}
\address{R.K., Department of Mathematics, Department of Physics and Astronomy, Purdue University}
\email{\href{mailto:rkaufman@purdue.edu}{rkaufman@purdue.edu}}

\author{Anibal~M.~Medina-Mardones}
\address{A.M-M., Max Plank Institute for Mathematics \and University of Notre Dame}
\email{\href{mailto:ammedmar@mpim-bonn.mpg.de}{ammedmar@mpim-bonn.mpg.de}}

@@

\begin{document}
	\input{aux/abstract}
	\maketitle
	\input{sec/introduction}
	\input{aux/acknowledgement}
	\input{sec/preliminaries}
	\input{sec/groups}
	\input{sec/operads}
	\input{sec/steenrod}
	\input{sec/effective}
	\input{sec/outlook}
	\printbibliography
\end{document}
